On the Synchronization of Computational RFIDs

### 2018-07-10 TMC-2017-11-0695.R1-main.tex
bio of all authors revised

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/ksy.jpeg}}]{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
received his Ph.D. degree in Computer Engineering from Ege University in 2012. He was a visiting scholar at the Department of Information Engineering, University of Padova in 2013. Between 2015 and 2017, he was a post-doctoral researcher at Embedded Software Group, Delft University of Technology. Currently, he is an assistant professor at the Department of Computer Engineering, Ege University and also a research affiliate with the Embedded Software Group at Delft University of Technology. His research interests are embedded systems and software, distributed algorithms, wireless sensor networks, energy harvesting systems and computational RFIDs.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/henko.jpg}}]{Henko Aantjes}
Henko Aantjes received his MSc degree in 201X. Currently he is a security evaluator at Brightsight BV, Delft, The Netherlands. His research interests include computational RFIDs, secure computation, and contactless payments.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{}
Biography text here.	
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
obtained his MSc degree in Computer Science from Delft University of Technology in 2015. Currently, he is a PhD candidate at the Embedded Software Group at Delft University of Technology. His research focuses on intermittent software architecture, (computational) RFIDs, backscatter technology, and wireless sensor networks.
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/sinan.jpg}}]{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
received his Ph.D. degree in Computer Engineering from Ege University, Izmir, Turkey, in 2012. He was a visiting scholar at the Department of Information Engineering, University of Padova in 2013. Between 2015 and 2017, he was a postdoctoral researcher at Embedded Software Group, Delft University of Technology, Delft, The Netherlands. Currently, he is an assistant professor at the Department of Computer Engineering, Ege University and also a research affiliate with the Embedded Software Group at Delft University of Technology. His research interests are embedded systems and software, distributed algorithms, wireless sensor networks, energy harvesting systems and computational RFIDs.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/henko.jpg}}]{Henko Aantjes}
Henko Aantjes received his MSc degree in 2016 from Delft University of Technology, Delft, The Netherlands. Currently he is a security evaluator at Brightsight BV, Delft, The Netherlands. His research interests include computational RFIDs, secure computation, and contactless payments.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{Przemys{\l}aw~Pawe{\l}czak} (S'03-M'10) received the MSc degree from Wroc{\l}aw University of Technology, Poland, in 2004 and the PhD degree from Delft University of Technology, The Netherlands in 2009.
 Between 2009 and 2011 he was a postdoctoral researcher at the Cognitive Reconfigurable Embedded Systems Lab, University of California, Los Angeles. Between 2012 and 2013 he was a research staff member at Fraunhofer Institute for Telecommunications, Heinrich Hertz Institute, Berlin, Germany. Since 2013 he is a (tenured) assistant professor at the Embedded Software Group of Delft University of Technology. His research interests include wireless networking, RFID systems and intermittently-powered embedded devices.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
obtained his MSc degree in 2015 from Delft University of Technology, Delft, The Netherlands. Currently, he is a PhD candidate at the Embedded Software Group at the same university. His research focuses on intermittent software architecture, (computational) RFIDs, and backscatter communication.
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage
